% mentors
I would like to thank my advisor Sergey Levine for his guidance over the past years.
The work in this thesis would not have been possible without his vision and support.
He was a source of inspiration, motivation, and pushed me to work on the hard problems that matter.
I have never met anyone more diligent or with so much commitment to excellence, and I was so lucky to have the opportunity to collaborate with him.

I would like to thank Pieter Abbeel for his mentorship.
Joining his lab after being inspired by a talk he gave shifted my life trajectory and motivated me to pursue a research career.
I would also like to thank Pulkit Agrawal for his mentorship, and for heavily influencing my thinking about robotics, machine learning, and research in general. I would like to thank Alison Gopnik and Alyosha Efros in addition to Sergey and Pieter for serving on my qualifying exam and thesis committee.

\vspace{5mm}

I would like to thank all my fantastic collaborators through the years.
First, I would like to thank my more senior collaborators who's wisdom and experience I benefited from immensely: Abhishek Gupta, Amy Zhang, Bob McGrew, Eugen Solowjow, Glen Berseth, Ilya Kostrikov, Jitendra Malik, Kuan Fang, Marcin Andrychowicz, Phillip Isola, and Wojciech Zaremba.
In particular, I would like to highlight Vitchyr Pong, who was my closest collaborator during my PhD.
I learned so much from working with him, and research really started to click for me once we started collaborating.
On top of being a great researcher and engineer, Vitchyr was also kind, encouraging, and a joy to work with.
I would also like to thank Shikhar Bahl, Murtaza Dalal, Sasha Khazatsky, Graham Hughes, Daniel Jing, Catherine Huang, Patrick Yin, Brian Zhu and Charles Xu specifically for the privilege of being a graduate mentor; I learned so much from the experience and it was one of the best parts of research for me.
And I would like to thank all the other collaborators who were instrumental in pursuing this research: Dian Chen, Gerrit Schoettler, Gokul Narayanan, Homer Walke, Jianlan Luo, Laura Smith, Matt Yan, Philippe Hansen-Estruch, Soroush Nasiriany, Steven Lin, Tobias Johannink.

% The lab
The Robotic AI and Learning Lab (RAIL) at Berkeley was an amazing place to be - I was surrounded by brilliant people and it felt like the state-of-the-art RL algorithms, important insider knowledge, and creative research perspectives were all just a few desks away at most.
For this I would like to thank Anusha Nagabandi, Anurag Ajay, Aravind Rajeswaran, Avi Singh, Aviral Kumar, Colin Li, Coline Devin, Dhruv Shah, Dibya Ghosh, Dinesh Jayaraman, Frederik Ebert, Greg Kahn, Kristian Hartikainen, Jason Peng, JD Co-Reyes, Justin Fu, Kate Rakelly, Katie Kang, Kelvin Xu, Laura Smith, Marvin Zhang, Michael Chang, Michael Janner, Natasha Jaques, Nick Rhinehart, Roberto Calandra, Rowan McAllister, Siddharth Reddy, Tuomas Haarnoja, Vikash Kumar, and Young Geng.
I will cherish all the great times, conversations, and conference trips we got to experience together.

Spending my entire academic career at Berkeley, the times I got to step away and imbibe new perspectives was always refreshing.
I would like to thank Marcin, Bob, Wojciech, and Pieter for my time at OpenAI which kickstarted my main research directions.
I would like to thank Tobias, Gerrit, and Eugen for the external collaboration with Siemens which drove me to think about RL from an applications point of view.
And I would like to thank Saurabh Gupta, Shubham Tulsiani, and Abhinav Gupta for their mentorship while at FAIR Pittsburgh; my time there really shifted my thinking about which ML problems are valuable to work on as well as about building research communities.

% Teachers
It takes a village to raise a child - I was lucky to have so many teachers and mentors in my life see potential in me, and go above and beyond their duty to help me and push me. I would like to thank them all, but especially David Petty, Peter Wolf, Robert Trakimas, Mike Hansen, Lauren Walsh, Amy Cooper, and Ms. Hunter for their dedication.

% Other people in grad school, and external collaborators
I am deeply grateful for the friends I made during graduate school, particularly Armin Askari, Ashish Kumar, Allan Jabri, Chandan Singh, Parsa Mahmoudieh, and Sasha Sax.
Playing basketball with Armin, Chandan, and Marvin was a vital source of sanity for me through the pandemic times.
I would like to thank Kelvin, Marvin, and Parsa for their support navigating the finish line of the PhD and searching for jobs.
I would also like to thank Sasha Sax and Nick Rhinehart for being thoughtful roommates and friends.

\vspace{5mm}

% Friends
I could not have done this work without the love and support of my friends.
I would like to thank Aditya Pradhan, Alexandria Lai, Alex Joo, Anna Apa, Brian Giang, Carlos Lazo, Greg Bulpitt, Jong Lim, Karthik Gururangan, Michael You, Nayif Alhomoud, Ryan Goh, Sid Moghe, Shuyang Ren, Sua Kim, and Sunny Zhang: I am so fortunate to have you all in my life.
Going further back, I would like to thank Donald Feng, George Zhang, Jessica Zhang, Kevin Gao, Ning Liu, Irene Wong, and Saavan Patel for their continued friendship.
I was lucky to share the last 13 (!) years of school with Saavan, and I deeply appreciate his support and loyalty throughout.

% Family
Finally, I would like to thank my family.
My entire extended family has been a source of comfort and well-wishes throughout this process and I am very grateful for their love and encouragement.
I would like to thank my grandparents Damodaran Nair, Sarada Damodaran Nair, Methil Somasundaram, and Chandramathi Panangadath for their love and care, for inspiring me, and for being excellent role models.
I would like to thank my father Vinod Nair for providing me with direction and purpose.
And I would like to thank my mother Asha Nair who inspired me with her love for others and sacrificed so much so that I could pursue my dreams.
